---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(tibble.print_min = 5, tibble.print_max = 5)
```

## Overview

dbgapr is a collection of functions that make it easier to organize, view, and use the phenotype data downloaded from the [dbGaP](https://www.ncbi.nlm.nih.gov/gap). 

## Installation

It is recommended to run dbgapr through [RStudio](https://www.rstudio.com/). The [table-viewer](https://support.rstudio.com/hc/en-us/articles/205175388-Using-the-Data-Viewer) available in recent versions of RStudio displays dataframe in a human friendly table view, which is perfect for browsing and filtering the dbGaP dataset and variable meta-info resulting from the dbgapr functions. The RStudio desktop version can be downloaded from [here](https://www.rstudio.com/products/rstudio/download). 

```{r, eval = FALSE}

# The dbgapr development version can be installed from GitHub:
# install.packages("devtools")
devtools::install_github("jameslhao/dbgapr_dev")
```

Please write to dbgap-help@ncbi.nlm.nih.gov for any problems or any questions. 

## Usage

More information of how to use dbgapr can be found from this [instruction](https://github.com/jameslhao/dbgapr_dev/blob/master/inst/doc/introduction.Rmd) on GitHub.


